Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2020-12-09 xrb2/paper.tex
some domain info

We present 6 simulations in total, summarized in
Table~\ref{table:runs}.  These simulations encompass 3 different
rotation rates: 250~Hz, 500~Hz, and 1000~Hz, and for the 500~Hz run, 4
different temperature profiles.  In the following subsections, we look
at how the flame properties depends on the model parameters.

>>>>

We present 6 simulations in total, summarized in
Table~\ref{table:runs}.  These simulations encompass 3 different
rotation rates: 250~Hz, 500~Hz, and 1000~Hz, and for the 500~Hz run, 4
different temperature profiles.  In the following subsections, we look
at how the flame properties depends on the model parameters.  All
simulations are run in a domain $1.8432\times 10^5~\mathrm{cm} \times
3.072\times 10^4~\mathrm{cm}$ with a coarse grid of $1152 \times 192$
zones and 2 levels of refinment (the first a jump by a factor of $4$
and the second a jump by a factor of $2$ finer).  This gives a
fine-grid resolution of $20~\mathrm{cm}$.  The entire atmosphere is
refined in these simulations, with the refinement tagging on all zones
with $\rho > 2.5\times 10^4~\gcc$.
